Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-07-27 Abstract.tex
Revise/improve abstract

Queries on big data collections are often more expensive than needed;
traditional databases optimize and incrementalize such queries but do not
support richly structured program data, or expressive programming languages
supporting higher-order functions. Manual optimization and incrementalization
interferes with program modularity and is often too error-prone to be feasible
or to enable maintenance of resulting programs.
In this thesis, we optimize and incrementalize such collection queries to free
programmers from such burdens.
Resulting programs are expressed in the same language, so that they can be
subjected to other standard optimizations.

>>>>

In modern programming languages, queries on in-memory collections are often more
expensive than needed.
While database queries can be readily optimized, collection queries often don't
translate trivially to databases, as modern programming languages are far more
expressive than databases, supporting both nested data and first-class functions.

Collection queries can be optimized and incrementalized by hand, but this
reduces modularity, and is often too error-prone to be feasible or to enable
maintenance of resulting programs.
In this thesis, we optimize and incrementalize such collection queries to free
programmers from such burdens.
Resulting programs are expressed in the same core language, so that they can be
subjected to other standard optimizations.
